---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
Scripts for extracting weather data from the Frost API: https://frost.met.no/index.html

# Make a client ID 
Select the "Create User" button here: https://frost.met.no/howto.html 
Save the client and secret ID somewhere safe. 

# Reference for how access FROST API through R 
https://frost.met.no/r_example.html 

# This has a weird bug in it but eventually would be good to understand how it works... 
https://git.nilu.no/rextapi/frostr

# List of different weather elements 
https://frost.met.no/elementtable 

## Manually search for weather stations 
https://senorge.no/ 




# Cool resource for finding global land / air datasets
https://ebas-data.nilu.no/Default.aspx



```{r}

# Libraries needed 
library(jsonlite)
library(tidyr)
library(frostr)
require(frostr)
library(plyr)
library(purrr)


## First, find the weather station(s) that you need. In this case, I want weather data as close as possible to the Marker wind park in Ørje - wind, temperature and precipitation. 

# This object stores all the sourceids and metadata for weather stations available through frost in Norway in Marker municipality 
findsources <- get_sources("0d4a9300-91f3-485c-a92f-e0ca9357b6c6", country = "NO", municipality = "MARKER", return_response = FALSE)
# Ørje E18 border station = SN1960 

# But where can I find wind data? 
findsources1 <- get_sources("0d4a9300-91f3-485c-a92f-e0ca9357b6c6", country = "NO", )


# Insert your own client ID here
client_id = '0d4a9300-91f3-485c-a92f-e0ca9357b6c6'

# Define Endpoint and parameters
endpoint <- paste0("https://", client_id, "@frost.met.no/observations/v0.jsonld")
sources <- 'SN1960, SN1950'
elements <- 'mean(air_temperature P1D),sum(precipitation_amount P1D),mean(wind_speed P1D)'
referenceTime <- '2020-07-01/2020-10-01'

# Build the URL to Frost
url <- paste0(
    endpoint, "?",
    "sources=", sources,
    "&referencetime=", referenceTime,
    "&elements=", elements
)
# Issue an HTTP GET request and extract JSON data
xs <- try(fromJSON(URLencode(url),flatten=T))

url
# Check if the request worked, print out any errors
if (class(xs) != 'try-error') {
    df <- unnest(xs$data)
    print("Data retrieved from frost.met.no!")
} else {
    print("Error: the data retrieval was not successful!")
}
# See results 
head(df)


# df1 <- unnest(xs$data[[2]])
# df2 <- rbind(xs$data)
# df3 <- rbind(df2$observations)
# df4 <- data.frame(xs$data)
# str(df4)



maybe <- cbind.data.frame(sourceId = as.character(xs$data$sourceId),
                          referencTime = as.character(xs$data$referenceTime),
                          do.call(rbind,lapply(xs$data$observations,function(x)unlist(x)[1:9])))


# Successfully extracted precipitation and temperature data but not wind... 


```

## Next 

Does work:
- max(air_temperature PT10M)
- sum(precipitation_amount P1D) 

### Doesn't work: 
- mean(wind_speed P1D)
- max(air_temperature PT1H)
- max(air_temperature PT12H)
- max(wind_speed P1D)
- max(wind_from_direction_of_gust PT10M)

## Troubleshooting: 
```{r}

# Define Endpoint and parameters
endpoint <- paste0("https://", client_id, "@frost.met.no/observations/v0.jsonld")
sources <- 'SN1960, SN1950'
elements <- 'max(air_temperature PT12H)'
referenceTime <- '2020-07-01/2020-10-01'

# Build the URL to Frost
url <- paste0(
    endpoint, "?",
    "sources=", sources,
    "&referencetime=", referenceTime,
    "&elements=", elements
)
# Issue an HTTP GET request and extract JSON data
xs <- try(fromJSON(URLencode(url),flatten=T))

url
# Check if the request worked, print out any errors
if (class(xs) != 'try-error') {
    df <- unnest(xs$data)
    print("Data retrieved from frost.met.no!")
} else {
    print("Error: the data retrieval was not successful!")
}
# See results 
head(df)


# df1 <- unnest(xs$data[[2]])
# df2 <- rbind(xs$data)
# df3 <- rbind(df2$observations)
# df4 <- data.frame(xs$data)
# str(df4)



maybe <- cbind.data.frame(sourceId = as.character(xs$data$sourceId),
                          referencTime = as.character(xs$data$referenceTime),
                          do.call(rbind,lapply(xs$data$observations,function(x)unlist(x)[1:9])))


```
## Time to try and collect model predictions of weather data 
https://github.com/BigelowLab/thredds


```{r}
## ALso not successful here, but can try again later: 

# library(devtools)
# install_github("BigelowLab/thredds")
# library(ncdf4)
# library(thredds)

```



