---
title: "Extract bat data for manual acoustic analysis"
output: html_document
date: "2023-10-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Extract processed bat acoustic data for manual acoustic analysis for Jackson and Emma's master theses - EcoForest 2023 

1.- Read the file paths of all files that match the file name pattern for output .wav files (000.wav)
2. - Subset data based on AutoIDs  
3. - Copy files into folders based on the AutoIDs (not including NOISE) into the P: 


# Prepare workspace and import data 
```{r}
library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(RColorBrewer)
library(cowplot)
library(readxl)

getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/EcoForest/EF"

## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/5. EcoForest/Data/Acoustics/Bat Acoustic Data/ROutputs"

file.name <- "ExportingBatAcousticData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today



# This contains the metadata as well as the AUTOids for all the processed files 

batmeta <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/5. EcoForest/Data/Acoustics/Bat Acoustic Data/ROutputs/EcoForest2023_NO_NOISE_AllProcessedBatDataCombined.csv", 
     col_types = cols(...1 = col_skip()))
# 17930 observations of 44 vars

names(batmeta)
#  [1] "INDIR"         "OUTDIR"        "FOLDER"        "IN.FILE"       "CHANNEL"       "OFFSET"        "DURATION"     
#  [8] "OUT.FILE.FS"   "OUT.FILE.ZC"   "DATE"          "TIME"          "HOUR"          "DATE.12"       "TIME.12"      
# [15] "HOUR.12"       "AUTO.ID."      "PULSES"        "MATCHING"      "MATCH.RATIO"   "MARGIN"        "ALTERNATE.1"  
# [22] "ALTERNATE.2"   "N"             "Fc"            "Sc"            "Dur"           "Fmax"          "Fmin"         
# [29] "Fmean"         "TBC"           "Fk"            "Tk"            "S1"            "Tc"            "Qual"         
# [36] "FILES"         "MANUAL.ID"     "ORGID"         "USERID"        "REVIEW.ORGID"  "REVIEW.USERID" "INPATHMD5"    
# [43] "OUTPATHMD5FS"  "OUTPATHMD5ZC" 

# All raw and processed bat data located here 
inputEF <-"P:/EcoForest/Acoustics"

# This will select the file path of all processed bat acoustic files which always have this same file ending (000.wav)
#my_files <- list.files(path = inputEF, pattern="000.wav", recursive = TRUE) # This is going to take an eternity. 
beep()

# #For some reason - had trouble getting data from this folder! 
# EF7CCB <- list.files(path = "P:/EcoForest/Acoustics/EF7-CC-B/WAV", pattern = "000.wav", recursive = TRUE) 
# EF7CCBdf <- as.data.frame(EF7CCB)
# # see down below how I fixed this.


# files_df <- as.data.frame(my_files)
# 43494 files 

#write.csv(files_df, file = file.path(output_today, "FilePathsALLProcessedBatData.csv"))
# Short cut! 
# stpred here for the next time so you do not have to find the file paths every time (it takes forever): 
files_df <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/5. EcoForest/Data/Acoustics/Bat Acoustic Data/ROutputs/ExportingBatAcousticData_2023-10-09/FilePathsALLProcessedBatData.csv")



```

## Create a list of file paths only for non noise files and then subset by autoid for copying into new folders 

```{r}

# Format the files_df and batmeta objects so it is possible to merge them with each other
names(files_df)
head(files_df)
#                                                                my_files
# 1 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_030000.wav
# 2 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_040000.wav
# 3 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_050000.wav
# 4 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_060000.wav
# 5 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_070000.wav
# 6 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_080000.wav

incols <- c("Site", "DATA", "Collection2", "Data", "Filename")

files_df1 <- files_df %>% 
  tidyr::separate(col = my_files,
                                        sep = "/",
                                       into = incols, 
                                       remove = FALSE)
head(files_df1)
#                                                               my_files      Site DATA          Collection2 Data
# 1 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_030000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
# 2 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_040000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
# 3 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_050000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
# 4 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_060000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
# 5 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_070000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
# 6 EF11-CC-A/DATA/19.07.2023_EF11-CC-A/Data/S4A16276_20230629_080000.wav EF11-CC-A DATA 19.07.2023_EF11-CC-A Data
#                       Filename
# 1 S4A16276_20230629_030000.wav
# 2 S4A16276_20230629_040000.wav
# 3 S4A16276_20230629_050000.wav
# 4 S4A16276_20230629_060000.wav
# 5 S4A16276_20230629_070000.wav
# 6 S4A16276_20230629_080000.wav 

batmeta$Filename <- batmeta$OUT.FILE.FS

head(files_df1$Filename)
# [1] "S4A16276_20230629_030000.wav" "S4A16276_20230629_040000.wav"
# [3] "S4A16276_20230629_050000.wav" "S4A16276_20230629_060000.wav"
# [5] "S4A16276_20230629_070000.wav" "S4A16276_20230629_080000.wav"   

head(batmeta$Filename)
# [1] "S4U12454_20230625_020014_000.wav" "S4U12454_20230628_235920_000.wav"
# [3] "S4U12454_20230625_234339_000.wav" "S4U12454_20230708_001208_000.wav"
# [5] "S4U12454_20230615_015652_000.wav" "S4U12454_20230614_231148_000.wav"    

filepaths <- files_df1 %>% select(Filename, my_files) %>% rename(filepaths = my_files) 


bats <- left_join(batmeta, filepaths)
head(bats)

bats <- bats %>% mutate(full_filepath = paste(inputEF, filepaths, sep = "/"))

head(bats$full_filepath)
# [1] "P:/EcoForest/Acoustics/EF2-NN-B/WAV/28.06.2023_EF2-NN-B/Data/S4U12454_20230625_020014_000.wav"  ## Looking good! 


### Check the NAs that failed to copy over: 
na_bat <- bats %>% filter(full_filepath == "P:/EcoForest/Acoustics/NA") 
## All the NAs are from the same site, but both of the existing collection points... 
# In theory, I should be able to recreate the file path 

head(na_bat$FOLDER)
# "DATA\\21.07.2023_EF7-CC-B\\Data"

 incols <- c("DATA", "Collection", "Data")

na_bat1 <- na_bat %>% 
  tidyr::separate(col = FOLDER,
                                        sep = "\\\\",
                                       into = incols, 
                                       remove = FALSE)

na_bat2 <- na_bat1 %>% mutate(fix = case_when(
  Collection == "21.07.2023_EF7-CC-B" ~ "P:/EcoForest/Acoustics/EF7-CC-B/WAV/DATA/21.07.2023_EF7-CC-B/Data",
  Collection == "03.07.2023_EF7-CC-B" ~ "P:/EcoForest/Acoustics/EF7-CC-B/WAV/DATA/03.07.2023_EF7-CC-B/Data"))

na_bat2 <- na_bat2 %>% mutate(fullpath = paste0(fix, "/", Filename)) 

 
#For some reason - had trouble getting data from this folder! 
EF7CCB <- list.files(path = "P:/EcoForest/Acoustics/EF7-CC-B/WAV", pattern = "000.wav", recursive = TRUE) 
EF7CCBdf <- as.data.frame(EF7CCB) # 436 obs 
EF7CCBdf <- EF7CCBdf %>% rename(Filename = EF7CCB) 
# see down below how I fixed this.

incols <- c("DATA", "Collection", "Data", "Filename")

na_bat <- EF7CCBdf %>% 
  tidyr::separate(col = Filename,
                                        sep = "/",
                                       into = incols, 
                                       remove = TRUE)

batmeta_EF7CCBdf1 <- batmeta %>% filter (str_detect(INDIR, pattern = "EF7-CC-B" )) # ## 97 observations 
batmeta_EF7CCBdf1$Filename <- batmeta_EF7CCBdf1$OUT.FILE.FS

na_bat1 <- left_join(na_bat, batmeta_EF7CCBdf1) # 
na_bat2 <- na_bat1 %>% drop_na(AUTO.ID.) # here is the missing metadata for the NA files! 

na_bat3 <- na_bat2 %>% mutate(fix = case_when(
  Collection == "21.07.2023_EF7-CC-B" ~ "P:/EcoForest/Acoustics/EF7-CC-B/WAV/DATA/21.07.2023_EF7-CC-B/Data",
  Collection == "03.07.2023_EF7-CC-B" ~ "P:/EcoForest/Acoustics/EF7-CC-B/WAV/DATA/03.07.2023_EF7-CC-B/Data"))

na_bat4 <- na_bat3 %>% mutate(fullpath = paste0(fix, "/", Filename)) 

names(bats)
names(na_bat5)
na_bat5 <- na_bat4 %>% select(-c(DATA, Collection, Data, fix))
na_bat5$full_filepath <- paste0(na_bat5$fullpath, "/", na_bat5$Filename)
head(na_bat5$full_filepath)

bats1 <- full_join(bats, na_bat5) # 18027 obs 
bats1 # now the missing NAs are added. 



## Need to see if these have been excluded from the rest of the manual acoustic analysis... 
```


## Subset by AUTOID and copy these files into their own folders 
```{r}

bats$AUTO.ID. <- as.factor(bats$AUTO.ID.)
direcs <- levels(bats$AUTO.ID.) # eventual new directories 
#  [1] "BARBAR" "EPTNIL" "EPTSER" "MYOBEC" "MYOBRA"
#  [6] "MYODAS" "MYODAU" "MYOMYO" "MYOMYS" "MYONAT"
# [11] "NYCLEI" "NYCNOC" "NoID"   "PIPPIP" "PIPPYG"
# [16] "PLEAUR" "PLEAUS" "VESMUR"

summary(bats$AUTO.ID.)
# BARBAR EPTNIL EPTSER MYOBEC MYOBRA MYODAS 
#    154   3676    437     18    826    527 
# MYODAU MYOMYO MYOMYS MYONAT NYCLEI NYCNOC 
#   2330     14   1586     35     26     64 
#   NoID PIPPIP PIPPYG PLEAUR PLEAUS VESMUR 
#   8022      6     25    160     19      5 

# Store metadata separately 
BARBAR <- bats %>% filter(AUTO.ID. == "BARBAR") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/BARBAR")
write.csv(BARBAR, "P:/EcoForest/Acoustics_ManualAnalysis/BARBAR/BARBAR_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
BARBAR_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/BARBAR/WAV"
BARBAR_my_files <- as.list(BARBAR$full_filepath)
BARBAR_my_files_list <- unlist(BARBAR_my_files)# 
head(BARBAR_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = BARBAR_my_files_list,
           to = BARBAR_dir)
 beep()
 
################################################################

EPTNIL <- bats %>% filter(AUTO.ID. == "EPTNIL") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/EPTNIL")
write.csv(EPTNIL, "P:/EcoForest/Acoustics_ManualAnalysis/EPTNIL/EPTNIL_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
EPTNIL_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/EPTNIL/WAV"
EPTNIL_my_files <- as.list(EPTNIL$full_filepath)
EPTNIL_my_files_list <- unlist(EPTNIL_my_files)# 
head(EPTNIL_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = EPTNIL_my_files_list,
           to = EPTNIL_dir)
 beep()
 
################################################################

EPTSER <- bats %>% filter(AUTO.ID. == "EPTSER") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/EPTSER/WAV")
write.csv(EPTSER, "P:/EcoForest/Acoustics_ManualAnalysis/EPTSER/EPTSER_meta.csv")

# Prepare to link and copy files to correct input and output directories 
EPTSER_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/EPTSER/WAV"
EPTSER_my_files <- as.list(EPTSER$full_filepath)
EPTSER_my_files_list <- unlist(EPTSER_my_files)# 
head(EPTSER_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = EPTSER_my_files_list,
           to = EPTSER_dir)
 beep()
 
################################################################


MYOBEC <- bats %>% filter(AUTO.ID. == "MYOBEC") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYOBEC/WAV")
write.csv(MYOBEC, "P:/EcoForest/Acoustics_ManualAnalysis/MYOBEC/MYOBEC_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYOBEC_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYOBEC/WAV"
MYOBEC_my_files <- as.list(MYOBEC$full_filepath)
MYOBEC_my_files_list <- unlist(MYOBEC_my_files)#
head(MYOBEC_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYOBEC_my_files_list,
           to = MYOBEC_dir)
 beep()
 
################################################################
 
MYOBRA <- bats %>% filter(AUTO.ID. == "MYOBRA") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYOBRA/WAV")
write.csv(MYOBRA, "P:/EcoForest/Acoustics_ManualAnalysis/MYOBRA/MYOBRA_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYOBRA_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYOBRA/WAV"
MYOBRA_my_files <- as.list(MYOBRA$full_filepath)
MYOBRA_my_files_list <- unlist(MYOBRA_my_files)#
head(MYOBRA_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYOBRA_my_files_list,
           to = MYOBRA_dir)
 beep()
 
################################################################

MYODAS <- bats %>% filter(AUTO.ID. == "MYODAS") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYODAS/WAV")
write.csv(MYODAS, "P:/EcoForest/Acoustics_ManualAnalysis/MYODAS/MYODAS_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYODAS_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYODAS/WAV"
MYODAS_my_files <- as.list(MYODAS$full_filepath)
MYODAS_my_files_list <- unlist(MYODAS_my_files)#
head(MYODAS_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYODAS_my_files_list,
           to = MYODAS_dir)
 beep()
 
################################################################

MYODAU <- bats %>% filter(AUTO.ID. == "MYODAU") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYODAU/WAV")
write.csv(MYODAU, "P:/EcoForest/Acoustics_ManualAnalysis/MYODAU/MYODAU_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYODAU_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYODAU/WAV"
MYODAU_my_files <- as.list(MYODAU$full_filepath)
MYODAU_my_files_list <- unlist(MYODAU_my_files)# 


# Copy files that match the file paths into a new folder. 
file.copy(from = MYODAU_my_files_list,
           to = MYODAU_dir)
 beep() 
 
 ## 10 files failed to copy... 
 
################################################################

MYOMYO <- bats %>% filter(AUTO.ID. == "MYOMYO") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYOMYO/WAV")
write.csv(MYOMYO, "P:/EcoForest/Acoustics_ManualAnalysis/MYOMYO/MYOMYO_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYOMYO_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYOMYO/WAV"
MYOMYO_my_files <- as.list(MYOMYO$full_filepath)
MYOMYO_my_files_list <- unlist(MYOMYO_my_files)# 154 elements
head(MYOMYO_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYOMYO_my_files_list,
           to = MYOMYO_dir)
 beep()
 
################################################################
 
 MYOMYS <- bats %>% filter(AUTO.ID. == "MYOMYS") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYOMYS/WAV")
write.csv(MYOMYS, "P:/EcoForest/Acoustics_ManualAnalysis/MYOMYS/MYOMYS_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYOMYS_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYOMYS/WAV"
MYOMYS_my_files <- as.list(MYOMYS$full_filepath)
MYOMYS_my_files_list <- unlist(MYOMYS_my_files)#
head(MYOMYS_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYOMYS_my_files_list,
           to = MYOMYS_dir)

## There were 9 files that did not copy over: 
## All from EF7-CC-B... 

# Warning messages:
# 1: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 2: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 3: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 4: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 5: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 6: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 7: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 8: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory
# 9: In file.copy(from = MYOMYS_my_files_list, to = MYOMYS_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\MYOMYS\WAV\NA: No such file or directory

 beep()
 
################################################################


MYONAT <- bats %>% filter(AUTO.ID. == "MYONAT") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/MYONAT/WAV")
write.csv(MYONAT, "P:/EcoForest/Acoustics_ManualAnalysis/MYONAT/MYONAT_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
MYONAT_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/MYONAT/WAV"
MYONAT_my_files <- as.list(MYONAT$full_filepath)
MYONAT_my_files_list <- unlist(MYONAT_my_files)# 154 elements
head(MYONAT_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = MYONAT_my_files_list,
           to = MYONAT_dir)
 beep()
 
################################################################

NYCLEI <- bats %>% filter(AUTO.ID. == "NYCLEI") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/NYCLEI/WAV")
write.csv(NYCLEI, "P:/EcoForest/Acoustics_ManualAnalysis/NYCLEI/NYCLEI_meta.csv")

# Prepare to link and copy files to correct input and output directories 
NYCLEI_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NYCLEI/WAV"
NYCLEI_my_files <- as.list(NYCLEI$full_filepath)
NYCLEI_my_files_list <- unlist(NYCLEI_my_files)# 154 elements
head(NYCLEI_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = NYCLEI_my_files_list,
           to = NYCLEI_dir)
 beep()
 
################################################################

NYCNOC <- bats %>% filter(AUTO.ID. == "NYCNOC") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/NYCNOC/WAV")
write.csv(NYCNOC, "P:/EcoForest/Acoustics_ManualAnalysis/NYCNOC/NYCNOC_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
NYCNOC_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NYCNOC/WAV"
NYCNOC_my_files <- as.list(NYCNOC$full_filepath)
NYCNOC_my_files_list <- unlist(NYCNOC_my_files)# 154 elements
head(NYCNOC_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = NYCNOC_my_files_list,
           to = NYCNOC_dir)
 beep()
 
 ## Check these 6 files: 
#  Warning messages:
# 1: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
# 2: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
# 3: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
# 4: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
# 5: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
# 6: In file.copy(from = NYCNOC_my_files_list, to = NYCNOC_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NYCNOC\WAV\NA: No such file or directory
 
################################################################

NoID <- bats %>% filter(AUTO.ID. == "NoID") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV")
write.csv(NoID, "P:/EcoForest/Acoustics_ManualAnalysis/NOID/NOID_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
NoID_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NoID/WAV"
NoID_my_files <- as.list(NoID$full_filepath)
NoID_my_files_list <- unlist(NoID_my_files)# 154 elements
head(NoID_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = NoID_my_files_list,
           to = NoID_dir)
 beep()
 
 # 48 files that did not copy over 
 # 
 # 48: In file.copy(from = NoID_my_files_list, to = NoID_dir) :
 #  problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\NoID\WAV\NA: No such file or directory
 
 ## Create a subset for Emma to classify which are 2500 random files from CC and NN 
 head(NoID$filepaths)
 
 incols <- c("Site", "WAV", "Collection", "Data", "Filename")

NoID1 <- NoID %>% 
  tidyr::separate(col = filepaths,
                                        sep = "/",
                                       into = incols, 
                                       remove = FALSE)
## NN sites 
 noid_nn <- NoID1 %>% filter(str_detect(Site, pattern = "NN"))
 noid_nn$Site <- factor(noid_nn$Site)
 table(noid_nn$Site)
# EF11-NN-B EF12-NN-B  EF2-NN-B  EF3-NN-B  EF4-NN-B  EF5-NN-B  EF6-NN-B  EF7-NN-B  EF8-NN-B 
#       456       395        31        12       175        97       216        81       185 
#  EF9-NN-B 
#       852 
 
 # Select 2500 random files from this 
 noid_nn1 <- noid_nn %>% sample_n(2500)
 table(noid_nn1$Site)
# EF11-NN-B EF12-NN-B  EF2-NN-B  EF3-NN-B  EF4-NN-B  EF5-NN-B  EF6-NN-B  EF7-NN-B  EF8-NN-B  EF9-NN-B 
#       456       395        31        12       175        97       216        81       185       852 
 

#dir.create("P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_NN")
#write.csv(noid_nn1, "P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_NN/NOID_subNN_meta.csv") 
 
NoID_NN_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_NN"
NoID_NN_my_files <- as.list(noid_nn1$full_filepath) 
NoID_NN_my_files_list <- unlist(NoID_NN_my_files)# 2500 elements
head(NoID_NN_my_files_list)

# file.copy(from = NoID_NN_my_files_list,
#            to = NoID_NN_dir)
#  beep()
#  
## Now for CC sites 
 noid_cc <- NoID1 %>% filter(str_detect(Site, pattern = "CC"))
 noid_cc$Site <- factor(noid_cc$Site)
 table(noid_cc$Site)
# EF11-CC-B EF12-CC-B  EF2-CC-B  EF3-CC-B  EF4-CC-B  EF5-CC-B  EF6-CC-B  EF8-CC-B  EF9-CC-B 
#       108      1915         9        18       442        95        21       207       572 
 
  ## Where is site 7? 

## MISSING DATA FROM EF7CC
## Deal with this later 
 
 # Select 2500 random files from this 
 noid_cc1 <- noid_cc %>% sample_n(2480) # Do 20 NoIDS from site 7 later 
 table(noid_cc1$Site)
# EF11-CC-B EF12-CC-B  EF2-CC-B  EF3-CC-B  EF4-CC-B  EF5-CC-B  EF6-CC-B  EF8-CC-B  EF9-CC-B 
#        75      1407         9        15       326        72        17       145       414 
 
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_CC_missingEF7")
write.csv(noid_cc1, "P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_CC_missingEF7/NOID_subCC_meta.csv") 
 
NoID_CC_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NOID/WAV_subset_CC_missingEF7"
NoID_CC_my_files <- as.list(noid_cc1$full_filepath) 
NoID_CC_my_files_list <- unlist(NoID_CC_my_files)# 2480 elements
head(NoID_CC_my_files_list)

file.copy(from = NoID_CC_my_files_list,
           to = NoID_CC_dir)
 beep()

################################################################

PIPPIP <- bats %>% filter(AUTO.ID. == "PIPPIP") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/PIPPIP/WAV")
write.csv(PIPPIP, "P:/EcoForest/Acoustics_ManualAnalysis/PIPPIP/PIPPIP_meta.csv")

# Prepare to link and copy files to correct input and output directories 
PIPPIP_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/PIPPIP/WAV"
PIPPIP_my_files <- as.list(PIPPIP$full_filepath)
PIPPIP_my_files_list <- unlist(PIPPIP_my_files)# 154 elements
head(PIPPIP_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = PIPPIP_my_files_list,
           to = PIPPIP_dir)
 beep()
 
 # Warning message:
# In file.copy(from = PIPPIP_my_files_list, to = PIPPIP_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PIPPIP\WAV\NA: No such file or directory

 
################################################################

PIPPYG <- bats %>% filter(AUTO.ID. == "PIPPYG") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/PIPPYG/WAV")
write.csv(PIPPYG, "P:/EcoForest/Acoustics_ManualAnalysis/PIPPYG/PIPPYG_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
PIPPYG_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/PIPPYG/WAV"
PIPPYG_my_files <- as.list(PIPPYG$full_filepath)
PIPPYG_my_files_list <- unlist(PIPPYG_my_files)# 154 elements
head(PIPPYG_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = PIPPYG_my_files_list,
           to = PIPPYG_dir)

 beep()
 
 # Warning messages:
# 1: In file.copy(from = PIPPYG_my_files_list, to = PIPPYG_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PIPPYG\WAV\NA: No such file or directory
# 2: In file.copy(from = PIPPYG_my_files_list, to = PIPPYG_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PIPPYG\WAV\NA: No such file or directory
# 3: In file.copy(from = PIPPYG_my_files_list, to = PIPPYG_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PIPPYG\WAV\NA: No such file or directory
# 4: In file.copy(from = PIPPYG_my_files_list, to = PIPPYG_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PIPPYG\WAV\NA: No such file or directory
 
################################################################

PLEAUR <- bats %>% filter(AUTO.ID. == "PLEAUR") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/PLEAUR/WAV")
write.csv(PLEAUR, "P:/EcoForest/Acoustics_ManualAnalysis/PLEAUR/PLEAUR_meta.csv") 

# Prepare to link and copy files to correct input and output directories 
PLEAUR_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/PLEAUR/WAV"
PLEAUR_my_files <- as.list(PLEAUR$full_filepath)
PLEAUR_my_files_list <- unlist(PLEAUR_my_files)# 154 elements
head(PLEAUR_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = PLEAUR_my_files_list,
           to = PLEAUR_dir)
 beep()
 
################################################################

PLEAUS <- bats %>% filter(AUTO.ID. == "PLEAUS") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/PLEAUS/WAV")
write.csv(PLEAUS, "P:/EcoForest/Acoustics_ManualAnalysis/PLEAUS/PLEAUS_meta.csv")

# Prepare to link and copy files to correct input and output directories 
PLEAUS_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/PLEAUS/WAV"
PLEAUS_my_files <- as.list(PLEAUS$full_filepath)
PLEAUS_my_files_list <- unlist(PLEAUS_my_files)# 154 elements
head(PLEAUS_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = PLEAUS_my_files_list,
           to = PLEAUS_dir)
 beep()
 
#  Warning message:
# In file.copy(from = PLEAUR_my_files_list, to = PLEAUR_dir) :
#   problem copying P:\EcoForest\Acoustics\NA to P:\EcoForest\Acoustics_ManualAnalysis\PLEAUR\WAV\NA: No such file or directory
 
################################################################

VESMUR <- bats %>% filter(AUTO.ID. == "VESMUR") %>% droplevels()
dir.create("P:/EcoForest/Acoustics_ManualAnalysis/VESMUR/WAV")
write.csv(VESMUR, "P:/EcoForest/Acoustics_ManualAnalysis/VESMUR/VESMUR_meta.csv")

# Prepare to link and copy files to correct input and output directories 
VESMUR_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/VESMUR/WAV"
VESMUR_my_files <- as.list(VESMUR$full_filepath)
VESMUR_my_files_list <- unlist(VESMUR_my_files)# 154 elements
head(VESMUR_my_files_list)

# Copy files that match the file paths into a new folder. 
file.copy(from = VESMUR_my_files_list,
           to = VESMUR_dir)
 beep()
 
################################################################
 
 



######################################

# 10 MYODAY Files 
na_MYODAU <- na_bat4 %>% filter(AUTO.ID. == "MYODAU")
write.csv(na_MYODAU, file = file.path(MYODAU_dir, "Missing_MYODAU_meta.csv")) 

na_MYODAU_my_files  <- as.list(na_MYODAU$fullpath)
na_MYODAU_my_files_list <- unlist(na_MYODAU_my_files)
head(na_MYODAU_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_MYODAU_my_files_list,
           to = MYODAU_dir)
 beep()

###################################### 

# 6 NYCNOC Files 
na_NYCNOC <- na_bat4 %>% filter(AUTO.ID. == "NYCNOC")
write.csv(na_NYCNOC, file = file.path(NYCNOC_dir, "Missing_NYCNOC_meta.csv")) 

na_NYCNOC_my_files  <- as.list(na_NYCNOC$fullpath)
na_NYCNOC_my_files_list <- unlist(na_NYCNOC_my_files)
head(na_NYCNOC_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_NYCNOC_my_files_list,
           to = NYCNOC_dir)
 beep()
 
######################################
 
  # 1 PIPPIP Files 
na_PIPPIP <- na_bat4 %>% filter(AUTO.ID. == "PIPPIP")
write.csv(na_PIPPIP, file = file.path(PIPPIP_dir, "Missing_PIPPIP_meta.csv")) 

na_PIPPIP_my_files  <- as.list(na_PIPPIP$fullpath)
na_PIPPIP_my_files_list <- unlist(na_PIPPIP_my_files)
head(na_PIPPIP_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_PIPPIP_my_files_list,
           to = PIPPIP_dir)
 beep()
 
######################################
 
  # 4 PIPPYG Files 
na_PIPPYG <- na_bat4 %>% filter(AUTO.ID. == "PIPPYG")
write.csv(na_PIPPYG, file = file.path(PIPPYG_dir, "Missing_PIPPYG_meta.csv")) 

na_PIPPYG_my_files  <- as.list(na_PIPPYG$fullpath)
na_PIPPYG_my_files_list <- unlist(na_PIPPYG_my_files)
head(na_PIPPYG_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_PIPPYG_my_files_list,
           to = PIPPYG_dir)
 beep()
 
######################################
 
# 1 PLEAUR Files 
na_PLEAUR <- na_bat4 %>% filter(AUTO.ID. == "PLEAUR")
write.csv(na_PLEAUR, file = file.path(PLEAUR_dir, "Missing_PLEAUR_meta.csv")) 

na_PLEAUR_my_files  <- as.list(na_PLEAUR$fullpath)
na_PLEAUR_my_files_list <- unlist(na_PLEAUR_my_files)
head(na_PLEAUR_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_PLEAUR_my_files_list,
           to = PLEAUR_dir)
 beep()
 
######################################
 
# 4 NoID Files 
na_NoID <- na_bat4 %>% filter(AUTO.ID. == "NoID")
write.csv(na_NoID, file = file.path(NoID_dir, "Missing_NoID_meta.csv")) 

na_NoID_my_files  <- as.list(na_NoID$fullpath)
na_NoID_my_files_list <- unlist(na_NoID_my_files)
head(na_NoID_my_files_list)

# Copy files that match the file paths into a new folder.
file.copy(from = na_NoID_my_files_list,
           to = NoID_dir)
 beep()
 
######################################




# 
# # Prepare to link and copy files to correct input and output directories
# test_dir<- "P:/EcoForest/Acoustics_ManualAnalysis/NA_bats/WAV"
# test_my_files <- as.list(test$fullpath)
# test_my_files_list <- unlist(test_my_files)#
# head(test_my_files_list)
# 
# head(test_my_files_list)
# 
# # Copy files that match the file paths into a new folder.
# file.copy(from = test_my_files_list,
#            to = test_dir)
#  beep()


```

## Check for duplicates in the mop up 
```{r}

# check_files <- list.files(path = "P:/EcoForest/Acoustics_ManualAnalysis/MYODAU/WAV", pattern="000.wav", recursive = TRUE) # This is going to take an eternity. 
# beep()
# 
# 
# check_df <- as.data.frame(check_files)
# dim(check_df)
# 
# test <- distinct(check_df)
# dim(test)
# 
# ## Good! 

```

