---
title: "InsertingZerosBatData"
output: html_document
date: "2023-09-15"
editor_options: 
  chunk_output_type: console
---


```{r}
library(readxl)
library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
library(kableExtra)
library(papeR)
library(skimr)
library(vtable)
library(ggdark)
library(RColorBrewer)
library(cowplot)
library(plotly)
library(hrbrthemes)
library(htmlwidgets)
library(viridis)
library(viridisLite)
library(cowplot)
library(ggplot2)
library(openair)
library(htmlwidgets)


## Import the processed data with site and plot type columns added by Jackson 
bats <- read_excel("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/5. EcoForest/Data/Acoustics/Bat Acoustic Data/ROutputs/BigBat4ColAllValues.xlsx", 
     col_types = c("skip", "text", "text", 
         "text", "text", "numeric", "numeric", 
         "numeric", "text", "text", "text", 
         "text", "numeric", "text", "text", 
         "numeric", "text", "numeric", "numeric", 
         "numeric", "numeric", "text", "text", 
         "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "text", "text", 
         "text", "text", "text", "text", "text", 
         "text", "text", "text", "text", "text"))
# View(bats)

dim(bats)  # 17930  48  (Jackson)
            ## 17930 15 (Reed)


getwd() # "C:/Users/jhell/Documents/Bats&Birds_EcoForest/Bat Acoustic Analysis"
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/EcoForest/EF"


## Setup output directory 
output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/5. EcoForest/Data/Acoustics/Bat Acoustic Data/ROutputs"

file.name <- "InsertingZerosBatData"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today

```


## Format the dataset
```{r Format the dataset}
bats1 <- bats %>%  
  mutate(across(c(AUTO.ID., LOCATION, SITETYPE, SITEPLOT), factor))

```



Create a data object that is just the nights when bats were recorded for each detector
```{r bats_nights_sum}

bat_sitemap <- bats1 %>% dplyr::select(LOCATION, SITETYPE, SITEPLOT) %>% distinct() 

# Aggregate numnber of bat passes per siteplot per night 
bats_nights_sum <- bats1 %>%
  group_by(SITEPLOT, DATE.12) %>% 
  dplyr::summarize(batpass = sum(n()))

head(bats_nights_sum)
#   siteplot DATE.12    batpass
#   <fct>    <date>       <int>
# 1 EF11-CC  2023-06-06      14
# 2 EF11-CC  2023-06-07      17
# 3 EF11-CC  2023-06-08       5
# 4 EF11-CC  2023-06-09      17
# 5 EF11-CC  2023-06-10       3
# 6 EF11-CC  2023-06-11      33

bats_nights_sum1 <- left_join(bats_nights_sum, bat_sitemap) #Attaches SITEPLOT, DATE.12, and batpass from bats_nights_sum to bat_sitemap
summary(bats_nights_sum1)
summary(bats_nights_sum1$SITEPLOT)

## Number of nights with bat passes for each siteplot 
# EF11-CC EF11-NN EF12-CC EF12-NN  EF2-CC  EF2-NN  EF3-CC  EF3-NN  EF4-CC  EF4-NN  EF5-CC  EF5-NN  EF6-CC  EF6-NN  EF7-CC 
#      24      35      21      29      10      26      12      15      30      30      30      31      24      28      21 
#  EF7-NN  EF8-CC  EF8-NN  EF9-CC  EF9-NN 
#      34      26      32      32      36 

#write.csv(bats_nights_sum1, "bat pass aggregated by night wout zeronights.csv")

batnights <- bats_nights_sum1
batnights$active.night <- "TRUE" #adds a new column "active.night" filled with TRUE
head(batnights)

#   siteplot DATE.12    batpass active.night
#   <fct>    <date>       <int> <chr>       
# 1 EF11-CC  2023-06-06      14 TRUE        
# 2 EF11-CC  2023-06-07      17 TRUE        
# 3 EF11-CC  2023-06-08       5 TRUE        
# 4 EF11-CC  2023-06-09      17 TRUE        
# 5 EF11-CC  2023-06-10       3 TRUE        
# 6 EF11-CC  2023-06-11      33 TRUE  

## Look for holes in the recording period: 

```


```{r Charts of activity/zeros}
# Use this plot as a map for detecting the sites that need checking
library(plotly)
library(hrbrthemes)
hrbrthemes::import_roboto_condensed()

#
 ggplot(batnights, aes(x=DATE.12, y=SITEPLOT, fill=batpass)) +  geom_tile()
 
 # Need to NOT include the 16 observations with totally off dates. 
 
 t <- batnights %>% filter(DATE.12 > "2023-05-01") # lost 5 nights 

 ggplot(t, aes(x=DATE.12, y=SITEPLOT, fill=batpass)) +  
   geom_tile() +
   theme(text = element_text(color = "black"),
         axis.text.y = element_text(color = "black"),
         axis.text.x = element_text(color = "black", size = 10, angle = -45,
                                    hjust = 0, vjust = 0)) +
   labs(x = "Date.12 (starts at noon)",
        y = "Siteplot",
        fill = "Sum of \nbatpasses")
 # Lots of gaps here! I imagine most are true zeroes, but we still need to check. 
 # Notice how EF4-CC and EF3-CC have a huge gap in July 
 
 # It easier to inspect these patterns using an interactive version of this map and I highly recommend doing this one site a time as well (makes your eyes cross less)
p <- ggplot(t, aes(x = DATE.12, y = SITEPLOT, fill = batpass)) +
          geom_tile() +
           theme_ipsum()
  
angleplot <- ggplot(t, aes(x = DATE.12, y = SITEPLOT, fill = batpass)) +
          geom_tile() +
           theme_ipsum() +
  labs(x = "Date.12 (starts at noon)",
        y = "Siteplot",
        fill = "Sum of \nbatpasses") +
  theme(text = element_text(color = "black", size = 11),
        axis.title.x = element_text(size = 13, face = "bold"),
        axis.title.y = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(color = "black", size = 11, angle = 0),
        axis.text.x = element_text(color = "black", size = 11, angle = -45))
   
ggplotly(angleplot)

pp <- ggplotly(angleplot)
pp

# htmlwidgets::saveWidget(as_widget(pp), file.path(output_today, "index_EF_NightCheck.html")) # exporting the figure (optional) 
#adds extra files - expost html from viewer instead

## Sitepairs 

pEF9 <- t %>% filter(SITEPLOT %in% c("EF9-NN-B", "EF9-CC-B")) %>% droplevels() %>% 
  ggplot(aes(x = DATE.12, y = SITEPLOT, fill = batpass)) +
          geom_tile() +
           theme_ipsum() +
  labs(x = "Date.12 (starts at noon)",
        y = "Siteplot",
        fill = "Sum of \nbatpasses") +
  theme(text = element_text(color = "black", size = 11),
        axis.title.x = element_text(size = 13, face = "bold"),
        axis.title.y = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(color = "black", size = 11, angle = 0),
        axis.text.x = element_text(color = "black", size = 11, angle = -45))

ppef9 <- ggplotly(pEF9)
ppef9 

htmlwidgets::saveWidget(as_widget(pp), file.path(output_today,"index_EF9_NightCheck.html"))


# write.csv(t, file = file.path(output_today, "EF_NightCheck_unedited.csv")) # keep a back up for editing 
# write.csv(t, file = file.path(output_today, "EF_NightCheck_formanualedit.csv")) # and another for manually editing (or if you want to do this in R - please do!!) Maybe Emma and Jackson can do 5 sites each? 

# USE THIS CSV TO MANUALLY INSERT NIGHTS WHEN THE DETECTORS WERE WORKING AND DEPLOYED BUT NO DATA WAS COLLECTED THE WHOLE NIGHT! 

```


```{r Editable ZeroFinderSitepair}
pEF12 <- t %>% filter(SITEPLOT %in% c("EF12-NN-B", "EF12-CC-B")) %>% droplevels() %>% 
  ggplot(aes(x = DATE.12, y = SITEPLOT, fill = batpass)) +
          geom_tile() +
           theme_ipsum() +
  labs(x = "Date.12 (starts at noon)",
        y = "Siteplot",
        fill = "Sum of \nbatpasses") +
  theme(text = element_text(color = "black", size = 11),
        legend.key.size = unit(1, 'cm'),
        axis.title.x = element_text(size = 13, face = "bold"),
        axis.title.y = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(color = "black", size = 11, angle = 0),
        axis.text.x = element_text(color = "black", size = 11, angle = -45))


ppEF12 <- ggplotly(pEF12)
ppEF12 

```

```{r ZeroFinderCharts without Viewer}
#save without needing to use the viewer
htmltools::save_html(html = ppEF4, file = "ppEF4zerofinder.html")

htmlwidgets::saveWidget(as_widget(pp), file.path(output_today,"index_EF9_NightCheck.html"))
```



```

## Next steps 

To go forward, you need two datasets: 

*active.nights* = a dataset with at least 3 columns: SITEPLOT, date.12, active.night. Active.night should only hold the value "TRUE" to indicate that on a given date and night, the detector was actually present, active and working.If a detector was deployed but not active on a certain date then there should simply not be a row for that siteplot with that date in this dataset. You will mostly need to go through and insert rows for dates and siteplots to account for nights when a detector was active but did not record anything. 

For equipment failures such as a tipped of detector (if this clearly impacted the recording abillities of the detector) or in the case of the detector with disrupted date/time settings,  you  may need to remove rows for dates when the detector collected a few bat passses but the recordings are no longer considered valid/part of the regular sampling effort (incomplete nights). 

*bats* = dataset of nightly aggregated bat data (for now, I recommend just aggregating all bats together regardless of autoid - we will have to redo this later to account for different species and behavior after manual id)
```
 
################################################
# Insert zero activity nights
################################################

```{r TESTING1: Import Excel file as Matrix}
library(utils)
truzero <- read.csv("ZeroFinder_NA_Truezero.csv", sep = ",", header = TRUE, row.names = 1)

truzero <- data.frame(truzero)
str(truzero) # works well - 48 obs (dates) of 20 variables (siteplots)
datecol <- as.factor(rownames(truzero))
siteplotcol <- as.factor(colnames(truzero))
#siteplotcol <- as.factor(colnames(truzero[-1])) # extracts all column names except the first (DATE.12)

summary(truzero)
glimpse(truzero)
str(truzero)
# dimension names DATE.12 and SITEPLOT to match with batnights 
# # DATE.12 as the string of rownames created; SITEPLOT as the string of column names 

dimnames <- list(SITEPLOT= colnames(truzero), DATE.12= rownames(truzero))
mat <- matrix(truzero, nrow = 48, ncol = 20, dimnames=dimnames)
mat
finaltable <- as.table(mat)
View(final)
# Error in matrix(truzero, nrow = 48, ncol = 20, dimnames = dimnames) : length of 'dimnames' [1] not equal to array extent
```



```{r TESTING2: Import Excel file as Matrix}
library(utils)
truzero <- read.csv("ZeroFinder_NA_Truezero.csv", sep = ",", header = FALSE)
truzero <- data.frame(truzero)
str(truzero) # works well - 48 obs (dates) of 20 variables (siteplots)
datecol <- as.factor(truzero[-1,1])
siteplotcol <- as.factor(truzero[1,-1])
#siteplotcol <- as.factor(colnames(truzero[-1])) # extracts all column names except the first (DATE.12)

summary(truzero)
glimpse(truzero)
str(truzero)
# dimension names DATE.12 and SITEPLOT to match with batnights 
# # DATE.12 as the string of rownames created; SITEPLOT as the string of column names 

dimnames <- list(siteplotcol, datecol)
mat <- matrix(truzero, nrow = 48, ncol = 20, dimnames=dimnames)
mat
finaltable <- as.table(mat)
View(final)
# creates 960 rows BUT 962 columns - we only want 3
```


```{r Brute force}
siteplotlist <- c(rep("EF2-CC-B", 48), rep("EF2-NN-B", 48),
                  rep("EF3-CC-B", 48), rep("EF3-NN-B", 48),
                  rep("EF488-CC-B", 48), rep("EF48-NN-B", 48),
                  rep("EF5-CC-B", 48), rep("EF5-NN-B", 48),
                  rep("EF6-CC-B", 48), rep("EF6-NN-B", 48),
                  rep("EF7-CC-B", 48), rep("EF7-NN-B", 48),
                  rep("EF8-CC-B", 48), rep("EF8-NN-B", 48),
                  rep("EF9-CC-B", 48), rep("EF9-NN-B", 48),
                  rep("EF11-CC-B", 48), rep("EF11-NN-B", 48),
                  rep("EF12-CC-B", 48), rep("EF12-NN-B", 48)
                  )
dateslist <- c(rep(seq(as.Date("2023-06-05"), as.Date("2023-07-22"), by="days"), 4)) 

#create table with 960 rows and 3 columns
empty <- as.table(matrix(0, nrow = 960, ncol = 3))


```

```{r Example conversion of matrix to dataframe}
data <- c(0.1, 0.2, 0.3, 0.3, 0.4, 0.5)
dimnames <- list(time=c(0, 0.5, 1), name=c("C_0", "C_1"))
mat <- matrix(data, ncol=2, nrow=3, dimnames=dimnames)
as.data.frame(as.table(mat))
```
  time name Freq
1    0  C_0  0.1
2  0.5  C_0  0.2
3    1  C_0  0.3
4    0  C_1  0.3
5  0.5  C_1  0.4
6    1  C_1  0.5


```{r TESTING: }
library(utils)
truzeroF <- read.csv("ZeroFinder_NA_Truezero.csv", sep = ",", header = FALSE)
truzeroF$DATE.12 <- format(as.POSIXct(truzero$DATE.12, format = '%Y-%m-%d'), format = '%Y-%m-%d') 
truzero <- read.csv("ZeroFinder_NA_Truezero.csv", sep = ",", header = TRUE, row.names = 1)
zeromatrix <- as.matrix(truzero)
glimpse(zeromatrix)
```





```{r Adding matrix values into batnights2}
batnights2 <- data.frame(batnights)
batnights2 <- batnights2 %>% 
  mutate(active.night = as.factor(active.night))
glimpse(batnights2)  # now active.night is a factor
# now need another column of NA, 0, or Data from ZeroFinger_NA_Truezero.csv
newnights <- read_delim("ZeroFinder_NA_Truezero.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE) # 48 obs of 21 var





```





```{r Adapting Example code from previous project}
# night = DATE.12 # Site = SITEPLOT
newnights <- read_delim("ZeroFinder_NA_Truezero.csv", 
     delim = ",", escape_double = FALSE, trim_ws = TRUE) # 48 obs of 1 var 

newnights1 <- newnights  %>%  
  mutate(DATE.12 = as.Date(DATE.12, "%d.%m.%Y")) 

sites <- colnames(newnights1[-1])

newnights1 <- newnights1 %>% 
  arrange(sites, DATE.12) %>% 
  mutate(active.night = as.factor(active.night), SITEPLOT = as.factor(sites))

str(newnights1)
summary(newnights1$Site)

```




Example code from a previous project - you will need to adapt this to your own data. 
Let me know when you get to this point and get confused / i realize it isn't easy for you to interpret scripts from a project you did not work on!

```{r}
# dat <- bats
# summary(dat)
#---- ADDING MISSING HOURS

# First, adjust dataset to include nights when detectors were active but no data was collected. 

# POST MANUAL EDITING IN EXCEL! - see bottom code chunk for more info on how this csv file was built. 

newnights <- Marker_night_inventory_0704_2022_edit <- read_delim("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/2. Marker 2019-2020/Marker 2022/Datasets/Marker_night_inventory_0704.2022_edit.csv", 
delim = ";", escape_double = FALSE, trim_ws = TRUE) # 951 obs of 3 vars 

newnights1 <- newnights  %>%  
  mutate(night = as.Date(night, "%d.%m.%Y")) %>%  
  arrange(Site, night) %>% 
  mutate(active.night = as.factor(active.night), Site = as.factor(Site))

str(newnights1)

summary(newnights1$Site)
# 
active.nights<- newnights1 %>% dplyr::select(Site, night) %>% unique() #951 nights all together
active.nights$active.night<-TRUE
# # Use existing dataset hours to create nighthour column for now. 
hours<-seq(min(dat$nighthour),max(dat$nighthour),3600) #--full daily sequence of hours for the entire study period
 hours<-hours[as.numeric(format(hours,"%H"))%in%sort(unique(as.numeric(format(dat$nighthour,"%H"))))]#--restrict to "nighthours" found in the data
# 
temp<-expand.grid(Site=unique(dat$Site),  nighthour=hours, guild = unique(dat$guild), behavior = unique(dat$behavior)) #----expanded data, 257664 obs of 4 vars 
temp$night <-  as.POSIXct(format(temp$nighthour,"%Y-%m-%d"),tz="UTC")
# 
temp2<-merge(temp,active.nights)
dim(temp2) # 170400 obs of 6 vars 
# 
temp3<-merge(temp2,dat,all.x=TRUE)
dim(temp3) # 170400 obs of 25 vars 
summary(temp3) # 165238 (previously 165224) NA obs 
# 
temp2<-merge(temp, active.nights) # 811 obs of 3 variables 
# 
summary(temp2$Site) # number of monitoring nights per site 
# # Met45 Met95   N02   N04   N08   N09   N10   N11   N14   P02   P04   P08   P09   P10   P11   P14 
#    70    70    59    44    60    48    60    60    60    60    60    60    60    60    60    60 
```

